Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
wording
typo
Rember the purpose of w* and fix the notation

The objective of the last step of our filtering procedure is to decrease the
importance of spikes that occur when there is a high global activity in the
network with respect to  spikes that occur during normal activity. Indeed, we
have conjectured that when a large part of the network is firing, the rate at
which observations are made is not high enough for being able to detect
interactions, and that it would therefore be preferable to lower their
importance by changing appropriately their magnitude. Additionally, it is
well-known that neurons may also spike because of a global high activity
\citep{stetter2012model}. In such  context, detecting pairwise neuron
interactions from the firing activity is meaningless. As such,
the signal output by $h$ is finally applied to the following function
\begin{align}
 w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}},
\end{align}
which effect is to magnify the importance of spikes that occur in case of low
global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance
around $t=4\text{s}$ in the figure. Note that the particular case where there
is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i)
= 1$.

@@

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since most timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened the difference in peak magnitude through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yield slightly AUROC with $c=0.9 \in (0, 1)$.

The magnification can also be optimized by adjusting differently the effect
depending on the global activity and the low-pass filter used. In that sense,
we introduce the following function
\begin{align}
 w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{m}
\end{align}
where $m$ is a piecewise linear function depending on the low-pass filter and
on the range of the global activity. We refer to our
implementation\footnote{available on \url{https://github.com/asutera/kaggle-
connectomics}.} for the values of the parameters and especially the parameter
$m$.

>>>>

The objective of the last step of our filtering procedure is to decrease the
importance of spikes that occur when there is a high global activity in the
network with respect to  spikes that occur during normal activity. Indeed, we
have conjectured that when a large part of the network is firing, the rate at
which observations are made is not high enough for being able to detect
interactions, and that it would therefore be preferable to lower their
importance by changing appropriately their magnitude. Additionally, it is
well-known that neurons may also spike because of a global high activity
\citep{stetter2012model}. In such  context, detecting pairwise neuron
interactions from the firing activity is meaningless. As such,
the signal output by $h$ is finally applied to the following function
\begin{align}
 w(x^{t}_i) &= (x^{t}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t}_j}}, \label{eq:magnify-filter}
\end{align}
which effect is to magnify the importance of spikes that occur in case of low
global activity (measured by $\sum_{j} x^{t}_j$), as observed for instance
around $t=4\text{s}$ in the figure. Note that the particular case where there
is no activity, i.e., $\sum_{j} x^{t}_j = 0$, is solved by setting $w(x^{t}_i)
= 1$.

@@

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened the difference in peak magnitudes through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yield slightly AUROC with $c=0.9 \in (0, 1)$.

After filter $c$, we applied a filter $w^*$ similar to $w$, whose goal is also
to magnify the importance of spikes that occur in case of low global activity.
Instead of equation \ref{eq:magnify-filter}, we had
\begin{align}
 w^*(x^{t}_i) &= {(x^{t}_i + 1 )^{\left (1 + \frac{1}{\sum_{j} x^{t}_j}\right )}}^{k(\sum_{j} x^{t}_j)}
\end{align}
where the function $k$ is a piecewise linear function optimized for each filter
$f_1$, $f_2$, $f_3$ and $f_4$. For more details on this aspect, we refer the
reader to the implementation \footnote{available on
\url{https://github.com/asutera/kaggle- connectomics}.}.
